Running RL algorithms on the aquarium environment to find unexpected biological insights

### 2020-11-17 guide/guide.tex
Add information regarding step() to guide.

The observation returned is structured as a dictionary with each shark as the
key and its respective observation as the value. Now, the observation includes
a few status informations about the shark itself but also the animals it sees.
For scalability, only a subset of animals can be observed, making the
environment a partially observable one. Specifically, the orientation (scaled
from radians to the range $[-1, 1]$) and the readiness to procreate ar
eincluded as status information. Next, distance and angle to each wall that is
in the view distance of the current shark is added. Since there are 4 walls,
this results in 8 values. If walls are disabled (i.e.\ a torus is used), the 8
values are replaced by zeroes. One of the main principles of the environment is
a consistent observation space, which is achieved by this sort of zero-padding.
Next, $n$ 3-tuple slots are used for sharks that may or may not be visible. $n$
is a hyperparameter that is set beforehand and stays constant throughout
training and evaluation. One 3-tuple slot consists of the distance to the other
shark, the angle to the shark and the orientation of the other shark. Sharks
that are outside of the visible range lead to zero-padding. After this, $m$
slots of the same structure are available for the fishes.

\subsection{Reward}
The environment returns a dictionary with sharks as keys and the reward
attained by the respective shark. The reward of a shark increases by $+10$ when
it eats a fish.

% Here step() return: obs, reward

% TODO: Partial observability.

>>>>

The observation returned is structured as a dictionary with each shark as the
key and its respective observation as the value. Now, the observation includes
a few status informations about the shark itself but also the animals it sees.
For scalability, only a subset of animals can be observed, making the
environment a partially observable one. Specifically, the orientation (scaled
from radians to the range $[-1, 1]$) and the readiness to procreate are
included as status information. Next, distance and angle to each wall that is
in the view distance of the current shark is added. Since there are 4 walls,
this results in 8 values. If walls are disabled (i.e.\ a torus is used), the 8
values are replaced by zeroes. One of the main principles of the environment is
a consistent observation space, which is achieved by this sort of zero-padding.
Next, $n$ 3-tuple slots are used for sharks that may or may not be visible. $n$
is a hyperparameter that is set beforehand and stays constant throughout
training and evaluation. One 3-tuple slot consists of the distance to the other
shark, the angle to the shark and the orientation of the other shark. Sharks
that are outside of the visible range lead to zero-padding. After this, $m$
slots of the same structure are available for the fishes.

\subsection{Reward}

The environment returns a dictionary with sharks as keys and the reward
attained by the respective shark. The reward of a shark increases by $+10$ when
it eats a fish.

\subsection{Step}

After a step in the environment, the standard 3-tuple known for gym
environments is returned. However, all three elements of that tuple are
dictionaries with sharks as keys and the observation, reward and done flag for
the respective shark as the value.

\subsection{Further Settings}

% TODO: Radius
